% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی، وارد کنید.
% توجه داشته باشید که جدول حاوی مشخصات پایان‌نامه/رساله، به طور خودکار، رسم می‌شود.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\baselineskip=.6cm
\begin{latin}
\latintitle{Analysis of brain data using graph neural networks}
\latinuniversity{Tarbiat Modares University}
\latinfaculty{Faculty of Mathematical Sciences}
\latindegree{Master in Computer Science}
%group:
\latinsubject{Department of Mathamatiics}
\latinfield{}
\latintitle{Vision Trnasformer}
\firstlatinsupervisor{Dr. Mansoor Rezghi }
%\secondlatinsupervisor{Second Supervisor}
%\firstlatinadvisor{First Advisor}
%\secondlatinadvisor{Second Advisor}
\latinname{Seyed Mohammad}
\latinsurname{Badzohreh}
\latinthesisdate{2024}
\latinkeywords{ }

\newpage
\thispagestyle{empty}
\baselineskip=.750cm
\en-abstract{%\noindent
Some data that present the time ...
}


%\markboth{\lr{Abstract}}{\lr{Abstract}}
\noindent
\begin{large}
\begin{center}
Abstract
\end{center}
\end{large}
%

In recent years, vision transformers have emerged as one of the core architectures in deep learning models for image processing. However, conventional designs of these transformers often rely on fully connected layers that require flattening high-order input tensors into vectors. This process not only leads to a significant increase in the number of parameters but also results in the loss of spatial structures and inter-dimensional relationships within the data. In this study, we propose a tensor-based framework for the design of a window-based vision transformer that leverages Tensor Compression Layers (TCL) and Tensor Regression Layers (TRL) to effectively model multilinear mappings across data dimensions. By preserving the multidimensional structure of images, the proposed method achieves a substantial reduction in the number of parameters while maintaining structural information and improving the interpretability of the model. Experimental results on standard benchmark datasets demonstrate that incorporating tensorized structures not only reduces computational complexity but also enhances classification accuracy.
\\
\newline
{{\bf Key Words:}} Vision Transformer, Tensor Decomposition, Tensor Compression Layer (TCL), Tensor Regression Layer (TRL), Multilinear Mapping, Image Classification, Deep Learning.%}
\newpage
\latinvtitle
%
%\latintitle{Analysis of brain data using graph neural networks}
%\latinuniversity{Tarbiat Modares University}
%\latinfaculty{Faculty of Mathematical Sciences}
%\latindegree{Master in Computer Science}
%%group:
%\latinsubject{Department of Mathamatiics}
%\latinfield{}
%\latintitle{Analysis of brain data using graph neural networks}
%\firstlatinsupervisor{Mansour Rezghi Ahagh}
%%\secondlatinsupervisor{Second Supervisor}
%%\firstlatinadvisor{First Advisor}
%%\secondlatinadvisor{Second Advisor}
%\latinname{Mitra}
%\latinsurname{Nemati Andavari}
%\latinthesisdate{2024}
%\latinkeywords{ }
\end{latin}
